Homework 8

### 2019-12-05 hw8/MSimonsHW8.tex
2b
Finished fixing hw8

\item Since $(x^7 + 25x^6 - 25x + 5)$ is a nonconstant polynomial in
$\mathbb{Q}$, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field if and only if
$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$.  We know that
$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$ by Eisenstein's
Criterion for prime $5$.  Thus, $\mathbb{Q}/(x^7 + 25x^6 - 25x + 5)$ is a field.

\item Consider $\mathbb{Z}/2\mathbb{Z}$.  If $f(x) = x^3 + 2x^2 - x + 1$, then
$\overline{f}(x) = x^3 - x + 1$.  We know that $\overline{f}(x)$ is
irreducible in $\mathbb{Z}/2\mathbb{Z}$ because
$\overline{f}(0) = \overline{f}(1) = 1$.  Since $\overline{f}(x)$ is
irreducible in $\mathbb{Z}/2\mathbb{Z}$, $f(x)$ is irreducible in $\mathbb{Q}$,
which means that $\mathbb{Q}[x]/(x^3 + 2x^2 - x + 1)$ is a field.

\item Only first-degree and second-degree polynomials can be irreducible in
$\mathbb{R}[x]$.  Since $(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$
is a fifth-degree polynomial, it is reducible in $\mathbb{R}[x]$.  Therefore
$\mathbb{R}[x]/(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$ is NOT
a field.

@@

\item
\begin{enumerate}
\item
Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible over
$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$ and $\deg f(x) = 3$.
Therefore,
$K$ is a field.

>>>>

\item Since $(x^7 + 25x^6 - 25x + 5)$ is a nonconstant polynomial in
$\mathbb{Q}$[x], $\mathbb{Q}[x]/(x^7 + 25x^6 - 25x + 5)$ is a field if and only if
$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$[x].  We know that
$(x^7 + 25x^6 - 25x + 5)$ is irreducible in $\mathbb{Q}$[x] by Eisenstein's
criterion for prime $5$.  Thus, $\mathbb{Q}[x]/(x^7 + 25x^6 - 25x + 5)$ is a field.

\item Consider $\mathbb{Z}/2\mathbb{Z}$.  If $f(x) = x^3 + 2x^2 - x + 1$, then
$\overline{f}(x) = x^3 - x + 1$.  We know that $\overline{f}(x)$ is
irreducible in $\mathbb{Z}/2\mathbb{Z}$ because
$\overline{f}(0) = \overline{f}(1) = 1$ and $\deg \overline{f}(x) = 3$.  Since $\overline{f}(x)$ is
irreducible in $\mathbb{Z}/2\mathbb{Z}$, $f(x)$ is irreducible in $\mathbb{Q}$,
which means that $\mathbb{Q}[x]/(x^3 + 2x^2 - x + 1)$ is a field.

\item Only first-degree and second-degree polynomials can be irreducible in
$\mathbb{R}[x]$.  Since $(x^5 + 42x^4 + \pi x^3 -1729x^2 + \ln (2)x - 2019)$
is a fifth-degree polynomial, it is reducible in $\mathbb{R}[x]$.  Therefore
$\mathbb{R}[x]/(x^5 + 42x^4 + \pi x^3 -1729x^2 + ln(2)x - 2019)$ is NOT
a field.

@@

\item
\begin{enumerate}
\item
Let $f(x) = x^3 + 2x + 1$.  We know that $f(x)$ is irreducible over
$\mathbb{Z}/3\mathbb{Z}$ because $f(0) = f(1) = f(2) = 1$ and $\deg f(x) = 3$.
Therefore,
$K$ is a field.
\item
We know that $f(t)$ does not have any roots in $K$ because $a \in \mathbb{Z}/3\mathbb{Z}$
is a root of $f(t)$ if and only if $t-a$ is a factor of $f(t)$.  By definition of
$\mathbb{Z}/3\mathbb{Z}$, $a$ can only be 0, 1, or 2.  However, by the Division
Algorithm,
\[
t^3 + 2t + 1 = t(t^2 + 2) + 1,
\]
\[
t^3 + 2t + 1 = (t+1)(t^2 - t) + 1,
\]
and
\[
t^3 + 2t + 1 = (t+2)(t^2 - 2t) + 1.
\]
Therefore, $f(t)$ has no roots.
